Machine Learning - Exercise 3

### 2021-02-20 exercise_3/paper/paper_ex3.tex
Updates from Overleaf

    Next, we select a model architecture of the copycat network. A possible problem with this approach is that we might not know the model architecture of the original network. However, this should not be a big problem as the knowledge can be copied to a different model.
    As pre-trained models tend to perform better, we used the VGG-16 architecture with pre-trained weights. It is obviously optimal if the pre-trained model is already close to the problem domain. In the next step we use the generated dataset to fit the pre-trained model.

    As described in~\cite{copycat} we will use Stochastic Gradient Descent with a Step Down policy for the learning rate for training the copycat model.

    \subsection{First Data set}
        As our first data set we combined the data sets described in the following two subsections. 
        %Since KDEF and AKDEF were one of the used data sets in the paper of Correia-Silva et al. we wanted to take them as validation that we achieve similar results. Unfortunately, they contain only about 5\,000 samples in total and we could not get access to other data sets used in the paper. Therefore, we combined them with a larger data set.
        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper. Therefore, we used different data sets and combined them to obtain a larger number of instances.

@@

    \subsection{Microsoft Azure Emotion API}
        As our first target model we chose the publicly available Microsoft Azure Emotion API. For an input image it returns a confidence across a set of emotions for each face in the image.

        This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
            \begin{itemize}
                \item Anger
                \item Contempt
                \item Disgust
                \item Fear
                \item Happiness
                \item Neutral
                \item Sadness
                \item Surprise
            \end{itemize}
        For example the following face from the publicly available Karolinska Directed Emotional Faces (KDEF) dataset, returned a vector that assigned a percentage of $0.999$ to Happiness $0.001$ to Surprise and $0$ to everything else.
            \begin{figure}[h!]
                    \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/AM18HAS.JPG}
                    \caption{A face classified as happy by Azure}
                    \label{fig:Happy_face}
            \end{figure}

        There is a free pricing option as well as a premium plan. As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan which allows us to submit up to 10 images per second.

        We started by stealing the model behind this API as it was already copied in the paper and as such we could assess whether the performance of our copied classifier was similar to the performance of the stolen classifier in the paper.

        Originally the plan was to add images, which are not part of the problem domain to the images to be classified by the blackbox, however as Azure does not classify images in which it does not recognise any faces, this was not possible.

        Testing the Azure Classifier using the prelabeled data from the Kaggled Competion we got an accuracy of $0.76$.

    \subsection{Evaluation 1}
        We used the Karolinska Directed Emotional Faces (KDEF) and Averaged Karolinska Directed Emotional Faces (AKDEF) dataset to query Azure as a Blackbox. As Azure did not recognise some of the faces we added No face detected as an additional class. \\

        The Cnn-Classifier was trained through by a Multi-layer perceptron. As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.\\

        In order to compare the performance of our copied classifier to the original we used the ..\todo[]{dataset}.

        \todo[]{graph}

    \subsection{Second Data Set}
        https://www.kaggle.com/crawford/cat-dataset 9000 Bilder

>>>>

    Next, we will select a model architecture of the copycat network. A possible problem with this approach is that we might not know the model architecture of the original network. However, this should not be a big problem as the knowledge can be copied to a different model.
    As pre-trained models tend to perform better, we will use the VGG-16 architecture with pre-trained weights. It is obviously optimal if the pre-trained model is already close to the problem domain.

    In the next step we will use the generated data set to fit the pre-trained model.
    As described in~\cite{copycat} we will use Stochastic Gradient Descent with a Step Down policy for the learning rate for training the copycat model.

    \subsection{First Data set}
        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper. Therefore, we used other data sets for our experiments. We combined two sets, which are described in the following two subsections, to obtain a larger number of instances.
        %As our first data set we combined the data sets described in the following two subsections. 
        %Since KDEF and AKDEF were one of the used data sets in the paper of Correia-Silva et al. we wanted to take them as validation that we achieve similar results. Unfortunately, they contain only about 5\,000 samples in total and we could not get access to other data sets used in the paper. Therefore, we combined them with a larger data set.

@@

    \subsection{Microsoft Azure Emotion API}
        As our first target model we used the publicly available Microsoft Azure Emotion API. For an input image this API returns a percentage vector of emotions for each face in the image. For each of the following emotions a value is assigned: 
        %This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
            \begin{itemize}
                \item Anger
                \item Contempt
                \item Disgust
                \item Fear
                \item Happiness
                \item Neutral
                \item Sadness
                \item Surprise
            \end{itemize}
        For example the face in Figure~\ref{fig:happy_face} from the publicly available KDEF dataset returned a vector that assigned a percentage of $0.999$ to happiness $0.001$ to surprise and $0$ to everything else.
            \begin{figure}[h!]
                    \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/AM18HAS.JPG}
                    \caption{Face classified as happy by Azure}
                    \label{fig:happy_face}
            \end{figure}

        In the Microsoft Azure Emotion API there is a free pricing option which allows us to submit up to 20 images per minute as well as a premium plan with up to 10 calls per second. As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan. %which allows us to submit up to 10 images per second.

        We started with stealing the model behind this API as it was already considered in the paper. Hence, we can assess whether the performance of our copied classifier is similar to the performance of the stolen classifier in the paper.

        Originally, we wanted to add instances, which are not part of the problem domain to our fake dataset. However, as Azure does not classify images in which it does not detect any face, this was not possible.

        Testing the Azure Classifier using the pre-labeled data from the Kaggle Competion we got an accuracy of $0.76$. \todo{in Evaluation}

    \subsection{Evaluation 1}
        We used the Karolinska Directed Emotional Faces (KDEF) and Averaged Karolinska Directed Emotional Faces (AKDEF) dataset to query Azure as a Blackbox. As Azure did not recognise some of the faces we added No face detected as an additional class. \todo{no face detected in 3.2}

        The CNN-Classifier was trained through by a Multi-layer perceptron. As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.

        In order to compare the performance of our copied classifier to the original we split the data set into a test and training set and looked at the accuracy resp. equality of our copied model, dependant on the size of the set used to train the model. We trained the model on progressively larger subsets of the training set, which were included in each other.

    \subsection{Second Data Set}
        Model: https://www.kaggle.com/c/dogs-vs-cats/data

        Attack and Test:

        https://www.kaggle.com/crawford/cat-dataset 9000 Bilder
